\clearpage
\tableofcontents
% \thispagestyle{plain} % 去掉页眉（可选）
\clearpage

\section{Introduction}
The scaling behavior of recommendation models has recently attracted significant attention \citep{OneRec, mtgr, HSTU, Wukong, URM, RankMixer, HLLM, OnePiece}, driven largely by the success of large language models (LLMs) in demonstrating predictable performance gains with increased model size \citep{GPT3, gpt4, deepseek, qwen2.5, mistral-7b, llama3, Llama2, Deepseek-r1}.
However, traditional recommendation models have struggled to exhibit similar scaling laws \citep{SASRec, GRU4Rec, Caser, SGL, survey_seq}.
These systems typically allocate the majority of parameters to large embedding tables for storing user and item representations, while using only inner-product or shallow scoring networks for final predictions.
Such an embedding-heavy design leads to performance plateaus: even as embedding dimensions or table sizes increase, improvements diminish quickly beyond moderate scales \citep{DIN, DCN, DCNv2, DeepFM}.

Generative recommendation offers a fundamental paradigm shift.
By compressing items into sequences of discrete Semantic IDs (SIDs) through quantization techniques \citep{rqkmeans, rqvae}, it uses compact vocabularies and redirects the bulk of parameters toward deep autoregressive Transformers that generate SID sequences \citep{TIGER, LCRec, TOKENRec, OneRec, OnePiece}.
This design enables scaling behaviors more characteristic of language models, where increased depth and capacity translate to consistent performance gains \citep{OneRec}.

Recent industrial deployments have demonstrated the promise of this generative paradigm.
OneRec \citep{OneRec, onerec-tech-v1} achieves significant improvements on Kuaishou's platform with 400 million daily active users, while OneRec-V2 \citep{onerec-tech-v2} further advances through lazy decoder architecture and preference alignment. 
OnePiece \citep{OnePiece} integrates LLM-style context engineering and reasoning into both retrieval and ranking models of industrial cascaded pipelines.
However, these results rely on massive proprietary datasets and remain closed-source, leaving critical questions unanswered for the research community:
\begin{itemize}
    \item Do the scaling advantages of generative recommendation transfer to public datasets?
    \item What is the minimal post-training recipe needed to achieve strong performance?
\end{itemize}



In this work, we present \textbf{MiniOneRec}, the first fully open-source framework for generative recommendation, which provides an end-to-end workflow encompassing SID generation, model supervised fine-tuning (SFT), and recommendation-driven reinforcement learning (RL). The release includes complete source code, reproducible training pipelines, and publicly available model checkpoints.
We implement SID construction using residual quantized variational autoencoder (RQ-VAE) \citep{rqvae}, in line with prior work such as TIGER \citep{TIGER, OneRec}.
We post-train Qwen-based (backbone) generative models at multiple scales, ranging from 0.5B to 7B parameters, on public benchmarks from the Amazon Review Dataset.
Following OneRec's successful two-stage post-training pipeline, we adopt SFT on user-item interaction sequences, followed by group relative policy gradient (GRPO) \citep{Deepseek-r1, deepseekmath} for alignment.
The main contributions of our work are summarized as follows:
\begin{itemize}
    \item \textbf{Validating the Scaling Laws of Generative Recommendation}:
    We present the first systematic investigation of how generative recommendation models scale on public data, to the best of our knowledge. Specifically, we train four MiniOneRec variants, spanning 0.5\,B to 7\,B parameters, on the Amazon Review corpus~\citep{amazon} with identical data splits and hyper-parameter settings. Both the final training loss and the held-out evaluation loss consistently decrease as model size grows (see Figures \ref{fig:scaling} Left and \ref{fig:scaling_eval_loss}), highlighting the superior parameter efficiency of the generative paradigm.
    \item \textbf{Optimizing Post-training Strategies for Generative Recommendation}: 
    We design a lightweight yet comprehensive post-training pipeline that tightly couples full-process SID alignment with reinforced preference optimization. First, we verify the influence of world knowledge on the model’s generative recommendation performance (see Figure \ref{fig:scaling} Right) and augment the vocabulary with dedicated SID tokens and enforce auxiliary alignment objectives throughout the two-stage optimization process. Second, during the RL phase, we shape the generation process itself: invalid tokens are masked to guarantee that every step produces a legal item, beam search is employed for efficient exploration of diverse candidates, and the reward signal combines rule-based accuracy with a ranking-aware penalty that pushes the model away from hard negatives. As a result, MiniOneRec offers a concise yet effective recipe for bringing RL with value-based ranking into generative recommendation, simultaneously improving candidate diversity and ranking fidelity.
\end{itemize}

The remainder of this report is organized as follows:
Section \ref{bg} reviews background on generative recommendation and the application of LLMs with RL in recommender systems.
Section \ref{method} presents our proposed MiniOneRec, including task formulation, item tokenization, and post-training pipeline.
Section \ref{training_detail} describes the training details while Section \ref{results} provides comprehensive experimental results.
Section \ref{conclusion} concludes with discussions of future directions.